---
title       : Cars and Earthquakes
subtitle    : Data Web App
author      : Spencer Chan
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Cars and Earthquakes

Information is everything nowadays, but handling the raw data is only half the necessary work.

Being able to present data in a presentable form is key in using the data for real world application.

--- .class #id 

## Cars

The mtcars data set contains the information of 32 different vehicles. This app lets you easily view which vehicles contain which number of cylinders by simply changing the input.


--- .class #id 

## Cars

The following code is the function which sorts out the vehicles with the matching number of cylinders

```{r}
cylfunction <- function(Value) rownames(mtcars[mtcars$cyl == Value,])
```


--- .class #id 

## Earthquakes

The quakes dataset is a list of 1000 earthquakes, containing location and magnitude values. This app lets you examine the distribution, and guess a mean value for the magnitude while providing a Mean Squared Error on your predicted mean.

---. class #id

## Earthquakes

The following is the formula used to calculate the MSE, followed by the code for the calculation and the display.

$$MSE = (x - \mu)^2$$

```{r}

# mse <- mean((quakes$mag - guess)^2)
# text(6,150, paste(" mu = ", guess))
# text(6,140, paste(" MSE = ", round(mse, 2)))

```
